{ \fontfamily{ptm}\selectfont First Order Nonsmooth Optimization: Algorithm Design, Variational analysis, and Applications }

### 2025-01-08 Notebook LaTEX/Proposal/main.tex
>w<, changes

@@

            $\blacksquare$ Add the bib for Mark Schmidt introductory paper RV methods.  
            \\ $\square$ Cite it. 
        }{\hl{See Gower's guide}} for more information on variance reduced methods in machine learning. 

@@

            $\blacksquare$ Add old Bertsekas's paper on incremental methods here. Paper: ``Incremental gradient, subgradient, and proximal methods for convex optimization: A survey''. 
            $\square$ Cite them. 
        {\hl{incremental methods}} \cite{bertsekas_incremental_2011,bertsekas_incremental_2017}

@@

        It can be deterministic, or stochastic. 

@@

        In each iteration, only the gradient of a few samples are accessed and uses simple calculations from previously stored gradient to attain overall better complexity.

@@

        \todoinline{\noindent
            We can then list some citations and references to commonly known variance reduced method here. 
            Let's list some here then. 
                \item[$\blacksquare$] SVRG: Proximal stochastic gradient with progressive variance reduction. 
                \item[$\blacksquare$] Finito: A faster, permutable incremental gradient method for big data problems
                \item[$\blacksquare$] SAG: Minimizing finite sums with the stochastic average gradient
                \item[$\blacksquare$] SAGA: A fast incremental gradient method with support for non-strongly convex composite objectives. 
        The parts coming will introduce the algorithms, explain its key innovations. 

@@

            The convergence proof (outer and inner loop together) from Lin was inspired by 
            \todo{\noindent
                $\blacksquare$ Add bib, the paper is 
                $\square$ Cite. 
            }{\hl{Schmidt's Inexact Proximal Gradient method. }} 
            The technique of estimating sequence as defined back in Definition \ref{def:nes-est-seq} did the heavy lifting, but it results in depressingly long proof making it unsuitable for exposition here. 

@@

                $\square$ Add paper: ``First-order methods of smooth convex optimization with inexact oracle'' \\
                $\square$ Cite them. 
            {\hl{Devolder et al.}}
            Their works were earlier and a Nesterov accelerated algorithm using estimating sequence and inexact oracles was derived. 
            Finally, besides Definition \ref{def:catalyst-termination-c1}, \ref{def:catalyst-termination-c2}, there is the ``Fixed Budget" termination criterion. 
            It terminates $\mathbb M$ after a fixed number of iteration. 

@@

            \begin{definition}[A better Catalyst Acceleration]\label{def:catalyst-relative}

@@

            \begin{theorem}[Outer loop complexity under criterion C2]\label{theorem:catalyst2-outer-loop}
                For the iterates $(x_k)_{k \ge 0}$ generated by algorithm in Definition \ref{def:catalyst-relative}, we have 
                \begin{enumerate}
                    \item If $\mu > 0$, choose $\alpha_0 = \sqrt{q}$, $\delta_k = \sqrt{q}/(2 - \sqrt{q})$. 
                    Then the iterates $(x_k)_{k \ge 0}$ satisfies $F(x_k) - F^* \le \mathcal O\left(1 - \sqrt{q}/2\right)^k$. 
                    \item If $\mu = 0$, choose $\alpha_0 = 1$, $\delta_k = 1/(k + 1)^2$ satisfies $F(x_k) - F^* \le \mathcal O(k^{-2})$. 
                \end{enumerate}
            \end{theorem}
            \begin{remark}
                This is Proposition 8, 9 in Lin et al.'s second Catalyst paper \cite{lin_catalyst_2018}.
                For a precise description of the upper bound, see Theorem 8. 
            \end{remark}
            The key improvement here compared to using absolute inexactness for $\mathbb M$ as stated by Theorem \ref{thm:err-seq-outer-s-cnvx}, \ref{thm:erro-seq-outer-cnvx} is that $(\delta_k)_{k \ge0}$ doesn't require knowledge on $F^*$. 
            This innocent detail helps to develop a nonconvex variant of Catalyst call 4WD Catalyst which is the focus of the paper by Paguette \cite{paquette_catalyst_2018}. 
            Corollary 16 in Lin et al.'s second Catalyst paper \cite{lin_catalyst_2018} gives complexity for $\mathbb M$ Using termination criterion C2 with a warm start specialized for $C2$. 
            It's important to note that the upper complexity bounds are much better, and it doesn't require bounded level set compared to Theorem \ref{prop:inner-loop-complexity-cnvx}.         
    \subsection{Potential future research}
        Now, we have enough context to understand the potential future directions of research regarding the Catalyst Acceleration framework.

>>>>

    \textbf{Organizations now follow}. 

@@

        See Gower's guide \cite{gower_variance-reduced_2020} for more information on variance reduced methods in machine learning. 

@@

        incremental methods

@@

        See Bertsekas's surveys \cite{bertsekas_incremental_2011,bertsekas_incremental_2017} on incremental method for more context. 
        VRM can be deterministic, or stochastic. 

@@

        In each iteration, the gradient of just a few samples are used with simple calculations to attain better complexity than full gradient descent. 

@@

        The parts coming introduce the Catalyst algorithms and its key innovations. 

@@

            The convergence proof (outer and inner loop together) from Lin was inspired by Schmidt's Inexact Proximal Gradient method \cite{schmidt_convergence_2011}. 
            The technique of estimating sequence introduced back in Definition \ref{def:nes-est-seq} did the heavy lifting, but it results in depressingly long proof making it unsuitable for exposition here. 

@@

            Devolder et al. \cite{devolder_first-order_2014}. 
            It's discusses a Nesterov accelerated algorithm using estimating sequence with inexact oracles. 
            Besides Definition \ref{def:catalyst-termination-c1}, \ref{def:catalyst-termination-c2}, the ``Fixed Budget" termination criterion terminates $\mathbb M$ after a fixed number of iteration given accuracy $\epsilon_k$. 

@@

            \begin{definition}[Catalyst Acceleration with relative inexactness]\label{def:catalyst-relative}

@@

            \begin{theorem}[Outer loop complexity under criterion C2]\label{theorem:catalyst2-outer-loop}
                For the iterates $(x_k)_{k \ge 0}$ generated by algorithm in Definition \ref{def:catalyst-relative}, we have 
                \begin{enumerate}
                    \item If $\mu > 0$, choose $\alpha_0 = \sqrt{q}$, $\delta_k = \sqrt{q}/(2 - \sqrt{q})$. 
                    Then the iterates $(x_k)_{k \ge 0}$ satisfies $F(x_k) - F^* \le \mathcal O\left(1 - \sqrt{q}/2\right)^k$. 
                    \item If $\mu = 0$, choose $\alpha_0 = 1$, $\delta_k = 1/(k + 1)^2$ satisfies $F(x_k) - F^* \le \mathcal O(k^{-2})$. 
                \end{enumerate}
            \end{theorem}
            \begin{remark}
                This is Proposition 8, 9 in Lin et al.'s second Catalyst paper \cite{lin_catalyst_2018}.
                For a precise description of the upper bound, see Theorem 8. 
            \end{remark}
            The key improvement here compared to using absolute inexactness for $\mathbb M$ as stated by Theorem \ref{thm:err-seq-outer-s-cnvx}, \ref{thm:erro-seq-outer-cnvx} is that $(\delta_k)_{k \ge0}$ doesn't require knowledge on $F^*$. 
            This innocent detail helps to develop a nonconvex variant of Catalyst call 4WD Catalyst which is the focus of the paper by Paquette \cite{paquette_catalyst_2018}. 
            Corollary 16 in Lin et al.'s second Catalyst paper \cite{lin_catalyst_2018} gives complexity for $\mathbb M$ Using termination criterion C2 with a warm start specialized for $C2$. 
            It's important to note that the upper complexity bounds are much better, and it doesn't require bounded level set compared to Theorem \ref{prop:inner-loop-complexity-cnvx}.         
    \subsection{Potential future research}
        Now, we have enough context to understand the potential future directions of research regarding the Catalyst Acceleration framework.
